Predicted cardiovascular risk for adults in the US with diabetes, chronic kidney disease, and ≥ 65 years of age

### 2021-04-15 docs/index.Rmd
no longer ignore html
add bp figs

style_duo_accent(
  primary_color = "#006341",
  secondary_color = "#CC8A00",
  inverse_header_color = "#FFFFFF"
)

@@

__Normal blood pressure__: systolic < 120 mm Hg and diastolic < 80 mm Hg

@@

__Elevated blood pressure__: systolic 120-129 mm Hg and diastolic < 80 mm Hg

@@

>>>>

style_duo_accent(
  primary_color = "#1E6B52",
  secondary_color = "#000000",
  inverse_header_color = "#CFC580"
)

@@

<span style="color:green"><b> Normal blood pressure</b></span>: systolic < 120 mm Hg and diastolic < 80 mm Hg

@@

<span style="color:blue"><b> Elevated blood pressure</b></span>: systolic 120-129 mm Hg and diastolic < 80 mm Hg

@@

```{r fig.width=8, fig.height=6, dpi=300}

p1 <- current_analysis$data %>%
  filter(bp_cat != 'Taking antihypertensive medication') %>%
  ggplot() +
  aes(x = bp_sys_mmhg, y = bp_dia_mmhg, col = bp_cat) +
  geom_point() +
  scale_color_manual(values = c("olivedrab3",
                                "darkturquoise",
                                "orange",
                                "red")) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        legend.position = 'top') +
  scale_x_continuous(breaks = c(120, 130, 140)) +
  scale_y_continuous(breaks = c(80, 90)) +
  labs(y = 'Diastolic blood pressure, mm Hg',
       x = 'Systolic blood pressure, mm Hg',
       color = '') +
  guides(colour = guide_legend(override.aes = list(size = 8)))

xlimits <- ggplot_build(p1)$layout$panel_scales_x[[1]]$range$range
ylimits <- ggplot_build(p1)$layout$panel_scales_y[[1]]$range$range

p1

```{r fig.width=8, fig.height=6, dpi=300}

current_analysis$data %>%
  filter(bp_cat == 'Stage 1 hypertension') %>%
  mutate(
    high_ascvd_risk = if_else(
      ever_had_ascvd == 'yes' | pcr_highrisk == 'yes',
      'High ASCVD risk',
      'Not high risk'
    )
  ) %>% 
  ggplot() +
  aes(x = bp_sys_mmhg, y = bp_dia_mmhg, col = high_ascvd_risk) +
  geom_point() +
  scale_color_manual(values = c("red", "orange")) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        legend.position = 'top') +
  scale_x_continuous(breaks = c(120, 130, 140), limits = xlimits) +
  scale_y_continuous(breaks = c(80, 90), limits = ylimits) +
  labs(y = 'Diastolic blood pressure, mm Hg',
       x = 'Systolic blood pressure, mm Hg',
       color = '') +
  guides(colour = guide_legend(override.aes = list(size = 8)))
